Title

### 2021-05-28 paper/main.tex
Fixed \ typo

Replacing Eqs.~(ref{eq:p-near})~and~(\ref{eq:p-free}) in
Eq.\~(\ref{eq:Aads-from-p}) we have an expression to calculate the
free energy of adsorption from a PMF of $\xi$, regardless of how the
PMF was obtained:

>>>>

Replacing Eqs.~(\ref{eq:p-near})~and~(\ref{eq:p-free}) in
Eq.\~(\ref{eq:Aads-from-p}) we have an expression to calculate the
free energy of adsorption from a PMF of $\xi$, regardless of how the
PMF was obtained:
